Algebraic properties of CFT coset construction and Schramm-Loewner evolution

### 2011-10-30 AffineLieAlgebras/SLE/article.tex
Text is finished, proofreading is required.

In the conclusion we compare classification of boundary condition changing operators which follows from martingale condition with general classification of b.c.c. operators in boundary conformal field theory related to D-brane solutions \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.

@@

When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}. 
For fields we have
\begin{equation*}
  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i}),
\end{equation*}
so additional term appears in the generator of field transformation. 
\begin{equation*}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)
\end{equation*}
Here $d\theta^{a}$ are the generators of $\mathrm{dim}\gf$-dimensional Brownian motion and $\mathbb{E}[d\theta^{a}d\theta^{b}]=\delta_{ab}dt$. We assume that $t^{a}$ is a basis of $\gf$ orthogonal with respect to Killing form $\mathcal{K}$, $\mathcal{K}(t^{a},t^{b})=\delta_{ab}$.

Using formula \eqref{eq:8} we get the equation from martingale condition:
\begin{equation*}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0,
\end{equation*}
where
\begin{equation*}
  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{\lambda_{i}}}{(w_{i}-z)^{n}}-\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}}
\end{equation*}
Again we can rewrite it as algebraic requirement for  field  which corresponds to boundary condition changing operator. Now
\begin{equation*}
  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
\end{equation*}
is level two null state and if we act on this state with raising operators we should get zero.
\begin{eqnarray}
  J^{a}_{1} \left|\psi\right>=0\\
  J^{a}_{2}\left|\psi\right>=0\\
  L_{2}\left|\psi\right>=0\\
  L_{1}\left|\psi\right>=0
\end{eqnarray}
Using commutation relations \eqref{eq:92} these equations can be rewritten as algebraic equations connecting parameters of random motion $\kappa, \tau$ with the level $k$ of affine Lie algebra representation. Rigorous analysis of these equations is given in the paper \cite{alekseev2010sle}.

@@

Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields  $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}. Here we are not interested in the details of this construction.

Looking at equation \eqref{eq:26} it is natural to think that we need to identify fields of $\gf$-model which differ by the action of $\afh$ generators $\tilde{J}_{n}^{b}$ to obtain primary fields of coset model. But the situation is not so simple since fields obtained in this way are equivalent if branching functions

For us it is only important that it is possible to obtain primary fields of coset model by field identification in WZNW-model with algebra $\gf\oplus \af$ \cite{fuchs1996resolution,schellekens1990field}.

(Field identification group here)

So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$. But some pairs are equivalent. This equivalence is given by the action of simple currents $(J,\tilde{J})$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.

Conformal weight of primary field is equal to
\begin{multline}
  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^v)}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
  \left|\phi_{\lambda}\right>=
  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
\end{multline}

%% So $G/A$-coset theory is related to $\gf\oplus \bar{\af}$-theory.

It is possible to obtain analogues of KZ-equations \cite{kogan1997knizhnik}:
\begin{equation*}
  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
\end{equation*}

@@

which can be rewritten as the requirement for
\begin{equation}
  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}J^{a}_{-1}J^{a}_{-1}\right)\right) \phi_{\Lambda}
\label{eq:10}
\end{equation}
to be level two null-field.

Here $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$. The equation \eqref{eq:10} is now
\begin{equation}
  \label{eq:11}
  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{\Lambda}
\end{equation}
If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\; J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
\begin{equation}
 \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{\Lambda}
\label{eq:12}
\end{equation}
which coincides with the equation for parafermionic fields introduced in paper \cite{santachiara2008sle}.

@@

Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
\begin{equation}
  \label{eq:13}
  L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{\Lambda}=0\quad \Longrightarrow\quad  (3\kappa-8) h_{\Lambda}+\frac{2(k-1)}{k+2}+\tau k =0
\end{equation}
Another equation can be obtained by action of $L_{1}^{2}$
\begin{equation}
  \label{eq:15}
  L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{\Lambda}=0
\end{equation}
Since $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$ we have

\begin{equation}
  \label{eq:17}
  12 h_{\Lambda}+2\kappa h_{\Lambda} (2h_{\Lambda}+1) +  \tau (C_{\Lambda}-\tilde{C}_{\Lambda})=0
\end{equation}

\begin{equation}
  \label{eq:16}
  \left(12 h_{\Lambda}+2\kappa h_{\Lambda} (2h_{\Lambda}+1) +  \tau (C_{\Lambda}-\Lambda^{2}\right) \phi_{\Lambda}=0
\end{equation}

We need to get one more equation since we have three variables $\kappa,\tau,h_{\Lambda}$. We can use that $\psi$ is singular vector so $L_{1}\psi=0$ and then
\begin{equation}
  \label{eq:18}
  J_{1}^{a}L_{1}\psi=0
\end{equation}

We can solve this equations.

Alternative approach is to study $\gf\oplus \af$ WZNW-model and then impose equivalence relations on the solutions. 
So we need to generalize the analysis of \cite{alekseev2010sle} to the case of semisimple Lie algebras.

From equation

Now consider as an example $\frac{SU(2)_{k}\times SU(2)_{1}}{SU(2)_{k+1}}$ -- another coset realization for minimal unitary models.

We get following relations on $\kappa,\tau$ and primary fields. So we see that the solutions at level $k$ are

Now we need to impose equivalence relations.

We get

Consider gauge transformation in gauged WZNW model:
\begin{eqnarray*}
  \delta \phi_{i}=(\epsilon_{L}^{a} t^{a}_{i}+\epsilon^{b}_{R}\tilde{t}^{b})\phi_{i}\\
  \delta A = -\partial \epsilon_{R}-[\epsilon_{R},A]
\end{eqnarray*}
Here $\epsilon_{L}, \epsilon_{R}$ are arbitrary holomorphic functions $\bar\partial\epsilon_{L,R}=0$. 
For  $\gf\oplus \af$ WZNW-model we can write SLE generator of primary field transformation under stochastic evolution as
\begin{equation*}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)+\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
\end{equation*}

%% \begin{equation*}
%%   \mathcal{G}_{i}^{L,R}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)\pm\sum_{b=1}^{\mathrm{dim} \af}\left(d \tilde{\theta} ^{b} \tilde{t}^{b}_{i}\right)\right)
%% \end{equation*}

and get martingale condition
\begin{equation*}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0
\end{equation*}

which can be rewritten as the requirement for
\begin{equation*}
  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}
\end{equation*}
to be level two null-field.

We can compare this result with the simplest possible coset model $su(2)/u(1)$ --  parafermion theory.

\subsection{Semisimple Lie algebras and coset construction}
\label{sec:semis-lie-algebr}

It is well known that unitary minimal models with central charge $c=1-\frac{6}{m(m+1)}$ can be obtained from coset construction starting with $su(2)_{m}\oplus su(2)_{1}$ WZW-model and factorizing it by $su(2)_{m+1}$. Here lower index represents level of affine Lie algebra representation.

In this case the dimension of Lie algebra $\gf=su(s)\oplus su(2)$ is 6, dual Coxeter number $h^{\vee}=2+2=4$.

\begin{equation}
  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
\label{eq:6}
\end{equation}

For semisimple Lie algebra $\gf=\gf_{1}+\gf_{2}$ with generators $J^{a}$ and $\tilde{J}^{b}$ correspondingly we can more explicitly write the relation \eqref{eq:6} as

\begin{equation*}
  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\left(\sum_{a} J^{a}_{-1} J^{a}_{-1}+\sum_{b}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right) \right) \left|\phi_{\Lambda}\right>    
\end{equation*}

This vector should be null vector of level two, so $L_{2}\left|\psi\right>=L_{1}\left|\psi\right>=0$. Then we get following algebraic relations for semisimple Lie algebra:
\begin{equation}
  \label{eq:7}
  \left( 3\kappa h_{\Lambda} +\frac{1}{2} \tau (k_{1} \mathrm{dim} \gf_{1}+k_{2}\mathrm{dim} \gf_{2}) -8 h_{\Lambda} - c\right)\phi_{\Lambda}=0
\end{equation}
SLE and factorization by equivalence relations.

%% \subsection{Parafermions}
%% \label{sec:parafermions}
%% 
%% $\mathbb{Z}(N)$ parafermions are equivalent to $SU(2)_{N}/U(1)$ coset theory.
%% 
%% It is well-known that parafermionic field can be written as product of $su(2)$-primary field and vertex operator of bosonic field. 
%% \begin{equation*}
%%   \Phi^{j}=\phi_{j}(z) \exp\left( -i \frac{j}{\sqrt{N}}\phi(z)\right)
%% \end{equation*}
%% where $\phi_{j}(z)$ is field of $SU(2)$-WZNW model with spin $j$, $\phi(z)$ -- $U(1)$ bosonic field.
%% 
%% For parafermionic current we have
%% \begin{equation*}
%%   \Psi^{\pm}=\frac{1}{\sqrt{N}} J^{\pm}\exp\left(\mp i \frac{1}{\sqrt{N}}\phi(z)\right)
%% \end{equation*}
%% %% Its action in terms of primary fields of $su(2)\oplus u(1)$ WZNW-model is equivalent to $J^{\pm}\pm \tilde{J}^{\pm}$.
%% %% !!! TODO
%% Martingale condition can be rewritten as
%% \begin{equation*}
%%   \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[\Psi^{+}_{-1}\Psi^{-}_{-1}+\Psi^{-}_{-1}\Psi^{+}_{-1}\right]\right) \left|\Phi\right>=0
%% \end{equation*}
%% which coincides with the result of Santachiara \cite{santachiara2008sle}.
%% 
%%

%% \subsection{Next steps}
%% 
%% Next steps in the study of SLE martingales for coset models  are the following. 
%% 
%% %At first we act on $  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum\limits_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}+\sum\limits_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\Lambda,\Gamma)}$ with  raising operators $J^{(a,b)}_{1}, J^{(a,b)}_{2}$ and get relations which connects level of representation and parameters of random motion $\kappa, \tau$. 
%% % !!! This is wrong !!!
%% % We can act by Sugawara generators 
%% 
%% Then we use Knizhnik-Zamolodchikov equations to rewrite the relations in simpler form and get conditions on possible boundary condition changing operators. 
%% 
%% Boundary states in coset models were actively studied. One of the ideas is to consider direct sum WZNW-model and use equivalence relations. This study is essentially the study representation of fusion algebra, Verlinde formula is one of key ingredients in this study. So we hope to compare the classification of boundary states obtained in this way with our condition on boundary condition changing operator. 
%% 
\section{Conclusion}
\label{sec:conclusion}

Now we see that it is possible to match SLE observables and CFT correlation functions. Martingale conditions can be seen as the constraints on possible Verma modules of affine Lie algebra corresponding to boundary condition changing operator. These Verma modules must have level two null state.

We can use primary fields of direct sum WZNW model and equivalence relations to study coset models.

Martingale conditions should be compared with the classification of boundary states with other methods.

>>>>

In the conclusion we discuss the need to compare classification of boundary condition changing operators which follows from martingale condition with general classification of b.c.c. operators in boundary conformal field theory related to D-brane solutions \cite{fuchs2005geometry,fredenhagen2002d,elitzur2002d,Maldacena:2001ky,felder1999geometry,alekseev1999d}.

@@

When we consider fields we need to add random gauge transformation (random motion in $G$) to stochastic evolution \cite{bettelheim2005stochastic}, \cite{alekseev2010sle}. 
For fields we have
\begin{equation*}
  d\phi_{\lambda_{i}}(w_{i}) = \mathcal{G}_{i}\phi_{\lambda_{i}}(w_{i}),
\end{equation*}
so additional term appears in the generator of field transformation. 
\begin{equation}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\sum_{a=1}^{\mathrm{dim} \gf}\left(d \theta ^{a} t^{a}_{i}\right)
\label{eq:18}
\end{equation}
Here $d\theta^{a}$ are the generators of $\mathrm{dim}\gf$-dimensional Brownian motion and $\mathbb{E}[d\theta^{a}d\theta^{b}]=\delta_{ab}dt$. We assume that $t^{a}$ is a basis of $\gf$ orthogonal with respect to Killing form $\mathcal{K}$, $\mathcal{K}(t^{a},t^{b})=\delta_{ab}$.

Using formula \eqref{eq:8} we get the equation from martingale condition:
\begin{equation}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{1}{2}\tau\sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)        \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}=0,
  \label{eq:27}
\end{equation}
where
\begin{equation*}
  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{\lambda_{i}}}{(w_{i}-z)^{n}}-\frac{1}{(w_{i}-z)^{n-1}}\partial_{w_{i}}\right);\quad \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}}
\end{equation*}
Again we can rewrite it as algebraic requirement for  field  which corresponds to boundary condition changing operator. Now
\begin{equation}
  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
  \label{eq:16}
\end{equation}
is level two null state and if we act on this state with raising operators we should get zero.
\begin{eqnarray}
  J^{a}_{1} \left|\psi\right>=0\\
  J^{a}_{2}\left|\psi\right>=0\\
  L_{2}\left|\psi\right>=0\\
  L_{1}\left|\psi\right>=0
\end{eqnarray}
Using commutation relations \eqref{eq:92} these equations can be rewritten as algebraic equations connecting parameters of random motion $\kappa, \tau$ with the level $k$ of affine Lie algebra representation. Rigorous analysis of these equations is given in the paper \cite{alekseev2010sle}.

@@

Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields  $A, \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}. Then fields are labeled by pairs of weights $(\mu,\nu)$, where $\mu$ is the weight of $\gfh$ and $\nu$ is the weight of $\afh$ correspondingly. But there are selection rules, i.e. the branching functions for certain pairs of weights $(\mu,\nu)$ vanish. There is also a redundancy, i.e. non-vanishing branching functions for distinct pairs $(\mu,\nu)$ turn out to be identical \cite{fuchs1996resolution,schellekens1990field}.

So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$  of algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$. Some pairs are equivalent. This equivalence is given by the action of so called ``simple currents'' $(J,\tilde{J})$, which are certain elements of outer  automorphisms group $\mathcal{O}(\gfh)\times \mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group G. We can think of simple currents as of primary fields and their action on fields of theory are given by fusion product \cite{difrancesco1997cft}.  Then we must primary fields of coset model are given by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where $(J,\tilde J)$ such that their conformal weights are equal:  $h_{J}-h_{\tilde{J}}=0$.

Conformal weight of primary field is equal to
\begin{multline}
  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b \tilde{J}^b_0 \tilde{J}^b_0 \right)
  \left|\phi_{(\mu,\nu)}\right>=\\
  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
\end{multline}
It is possible to obtain analogues of KZ-equations for coset models \cite{kogan1997knizhnik}:
\begin{equation*}
  \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots \phi_{N}(z_{N})\right>=0
\end{equation*}

@@

which can be rewritten as the requirement for
\begin{equation}
  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf-\mathrm{dim}\af}J^{a}_{-1}J^{a}_{-1}\right)\right) \phi_{(\mu,\nu)}
\label{eq:10}
\end{equation}
to be level two null-field.

Here $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator $J^{3}$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$. We label weights by Dynkin labels, so $J^{3}_{0}\phi_{(\mu,\nu)}=\frac{\mu}{2} \phi_{(\mu,\nu)}$.

 The equation \eqref{eq:10} is now
\begin{equation}
  \label{eq:11}
  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
\end{equation}
If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\; J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
\begin{equation}
 \psi= \left(-2 L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right) \phi_{(\mu,\nu)}
\label{eq:12}
\end{equation}
which are similar to the equations for parafermionic fields introduced in paper \cite{santachiara2008sle}.

@@

Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
\begin{equation}
  \label{eq:13}
  L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
\end{equation}
and obtain
\begin{equation}
  \label{eq:28}
  (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
\end{equation}
Another equation can be obtained by action of $L_{1}^{2}$
\begin{equation}
  \label{eq:15}
  L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
\end{equation}
Since $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$ we have
\begin{equation}
  \label{eq:17}
  12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) +  \tau (C_{\mu}-\tilde{C}_{\nu})=0,
\end{equation}
where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator $\sum_{a}t^{a}t^{a}$. For $u(1)$ it is just $\nu^{2}$.
We need to get one more equation since we have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so $L_{1}\psi=0$ and then $J_{1}^{3}L_{1}\psi=0$, so
\begin{equation}
  \label{eq:29}
  \left(-6  + \kappa +  \tau +  2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0} \phi_{(\mu,\nu)}=0
\end{equation}

Turn to the case $k=2, \;c=1/2$ which corresponds to square lattice Ising model. We have three non-equivalent fields numbered by the pairs of $su(2)$ and $u(1)$ weights, which are $\phi_{(0,0)}, \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$.
The equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations \eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in context of the Ising model. If we consider the field $\phi_{(1,1)}$ we have no solution for $\kappa,\tau$, so we see that not every primary field correspond to some boundary condition changing operator.

Now let us generalize to arbitrary coset model. It is not always convenient to work with generators orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley or Cartan-Weyl basis. So we introduce additional $\mathrm{dim}\gf$-dimensional Brownian motion \eqref{eq:18} with the normalization condition $\mathbb{E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$. We need to consider Brownian motion on factor space $G/A$, the generator of field transformation \eqref{eq:2} is
\begin{equation*}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right)
\end{equation*}
and we get \eqref{eq:8} martingale condition, which can be written as
\begin{equation*}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0.
\end{equation*}
This equation can be rewritten as the requirement for
\begin{equation}
  \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\mathrm{dim}\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\mathrm{dim}\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right) \phi_{(\mu,\nu)}
\label{eq:30}
\end{equation}
to be level two null-field.

Acting on \eqref{eq:30} with $L_{2}$ and $L_{1}^{2}$ we can obtain equations \eqref{eq:28} and \eqref{eq:17}. To get more equations we can act by $\afh$-generators $\tilde{J}^{b}_{1}$ and $L_{1}$ similarly to what was done with $J^{3}_{1}$ to get equation \eqref{eq:29}.

To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} as was done for WZNW-models in paper \cite{alekseev2010sle}.

\section{Conclusion}
\label{sec:conclusion}

We proposed a way to generalize Schramm-Loewner evolution to obtain observables which can be studied by methods of coset conformal field theory. The description of fields in coset models is not very simple due to field identification \cite{schellekens1990field} and the need of resolution of fixed points \cite{Fuchs:1996dd,fuchs1996resolution} which we have not discussed here. This subtleties can complicate the solution of equations  \eqref{eq:28}, \eqref{eq:17} and analogues of equation \eqref{eq:29}. On the other hand the use of Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} for correlation functions in the spirit of \cite{alekseev2010sle} lead to matrix algebraic relations which are similar to NIM-representations for boundary states \cite{ishikawa2003novel}. The study of this subject can reveal deep algebraic connection of martingale conditions with boundary states classification.

Physical interpretation of the solutions of martingale conditions is not clear, but there is also no lattice interpretation of Schramm-Loewner evolution with additional Brownian motion on group manifold \cite{bettelheim2005stochastic} and no lattice interpretation of WZNW-models. We think that these questions are closely related.
\newpage
